Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-19 paper/v1.0/sections/4_inverse_scattering_time.tex
Correcting effective mass

Normalized energy band broadening against ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and results are given in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}). To make comparison we have selected the experiment parameters to match with analysis done in Ref.~\cite{endo09}. In their study, they have assumed that the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$. Therefore in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
Here we can identify that we can change the each Landau level normalized energy broadening value using apllied electromagnetic field. When the applied field's intensity increase the energy broadening gets reduced which make changes in conductivity of 2DEG.

>>>>

Normalized energy band broadening against ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and results are given in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}). To make comparison we have selected the experiment parameters to match with analysis done in Ref.~\cite{endo09}.
In their study, they have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e = 0.07m$ where $m$ is mass of the electron \cite{endo09,winkler03,wackerl20} and the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$. Therefore in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
Here we can identify that we can change the each Landau level normalized energy broadening value using apllied electromagnetic field. When the applied field's intensity increase the energy broadening gets reduced which make changes in conductivity of 2DEG.

### 2021-07-19 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Rearrange the sections and names
Correcting effective mass

A general theory for the conductivity in dressed systems with the disorder averaging was introduced by M. Wackerl in Ref.~\cite{wackerl20,wackerlthesis20}. Within this theory, the general $x$-directional longitudinal DC limit conductivity can be express with
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg].
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ th Fourier component (see Appendix D) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectvely defined against the Floquet modes of the considering system. Here we have assumed that only $s=0$ th Fourier component of the current operator is contributing to the conductivity. In addition $A$ is the area of the considering two-dimentionl system, partical distribution function is given by $f$ and $\lambda$ is a function that can be choose such that
\begin{equation} \label{eq_21}
    \lambda - \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \lambda + \frac{\hbar \omega}{2},
\end{equation}
where $ \varepsilon_N$ are quasienergies of all considering Floquet states.

>>>>

% Section 05 - Floquet-Drude Conductivity in Quantum Hall Systems

A general theory for the conductivity in dressed systems with the disorder averaging was introduced by M. Wackerl in Ref.~\cite{wackerl20,wackerlthesis20}. Within this theory, the general $x$-directional longitudinal DC limit conductivity can be express with
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg].
  \end{aligned}
\end{equation}

\noindent
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ th Fourier component (see Appendix D) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectvely defined against the Floquet modes of the considering system. Here we have assumed that only $s=0$ th Fourier component of the current operator is contributing to the conductivity. In addition $A$ is the area of the considering two-dimentionl system, partical distribution function is given by $f$ and $\lambda$ is a function that can be choose such that
\begin{equation} \label{eq_21}
    \lambda - \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \lambda + \frac{\hbar \omega}{2},
\end{equation}
where $ \varepsilon_N$ are quasienergies of all considering Floquet states.
